Article Title

### 2022-04-22 paper/main/02_methods.tex
style(refractor-project-by-updated-workflow): refactor the project by updated workflow
BREAKING CHANGE:
refactor(config.py-processing.py-values.py-statistic.py): refactor in formats

	% 计算贡献度
	\subsection{Contribution decomposition}
		We decomposed the amount of variation in each index at different periods in order to quantify the contribution of each influence to the index. Using the Integrated Water Resources governance (IWGI) Index as an example, its value is influenced by normalized indicators in three dimensions: stress ($I'_S$), purpose ($I'_P$) and allocation ($I'_C$). We can calculate their differences between two certain years ($y_2$ and $y_1$, $y_2 > y_1$) by:
		\begin{align}
		\Delta IWGI &= (I'_{P_{y_2}} + I'_{C_{y_2}} - I'_{S_{y_2}}) - (I'_{P_{y_1}} + I'_{C_{y_1}} - I'_{S_{y_1}}) \\
		&= (I'_{P_{y_2}} - I'_{P_{y_1}}) + (I'_{C_{y_2}} - I'_{C_{y_1}}) + (I'_{S_{y_1}} - I'_{S_{y_2}}) \\
		&= \Delta I'_P + \Delta I'_C + (-\Delta I'_S)
		\end{align}
		Then, the contribution of dimension $x$ to IWGI's changes can be referred as:
		\begin{equation}
			Contribution_x = \frac{\Delta I'_x}{|\Delta IWGI|}
		\end{equation}

>>>>

	% 计算贡献度
	\subsection{Contribution decomposition}
		We decomposed the amount of variation in each index at different periods to quantify each influence's contribution to the index. Using the Integrated Water Resources governance (IWGI) Index as an example, its value is influenced by normalized indicators in three dimensions: stress ($I'_S$), purpose ($I'_P$) and allocation ($I'_C$). We can calculate their differences between two certain years ($y_2$ and $y_1$, $y_2 > y_1$) by:
		\begin{align}
		\Delta IWGI &= (I'_{P_{y_2}} + I'_{C_{y_2}} - I'_{S_{y_2}}) - (I'_{P_{y_1}} + I'_{C_{y_1}} - I'_{S_{y_1}}) \\
		&= (I'_{P_{y_2}} - I'_{P_{y_1}}) + (I'_{C_{y_2}} - I'_{C_{y_1}}) + (I'_{S_{y_1}} - I'_{S_{y_2}}) \\
		&= \Delta I'_P + \Delta I'_C + (-\Delta I'_S)
		\end{align}
		Then, the contribution of dimension $x$ to IWGI's changes can be referred to as:
		\begin{equation}
			Contribution_x = \frac{\Delta I'_x}{\lvert \Delta IWGI \rvert}
		\end{equation}
